\section*{NeurIPS Paper Checklist}

\begin{enumerate}

\item {\bf Claims}
    \item[] Question: Do the main claims made in the abstract and introduction accurately reflect the paper's contributions and scope?
    \item[] Answer: \answerYes{}
    \item[] Justification: The abstract and introduction state four contributions: a labelled dataset built from raw OCR'd \textit{professions de foi}, a before/after lexical-cleaning comparison that exposes what TF-IDF actually classifies on, a data-efficient linear probe on frozen sentence-CamemBERT embeddings as a control for end-to-end fine-tuning, and a temporal-split evaluation paired with a geometric look at the sentence-transformer embeddings (t-SNE, UMAP, silhouette score).

\item {\bf Limitations}
    \item[] Question: Does the paper discuss the limitations of the work performed by the authors?
    \item[] Answer: \answerYes{}
    \item[] Justification: Section~\ref{sec:discussion} discusses residual candidate/toponym leakage after v2 cleaning, regex labelling bias (which also explains the small Extr\^{e}me droite training set), uneven OCR quality, the 512-token truncation that penalises both the fine-tuned CamemBERT and the linear probe, the absence of continued masked-language-model pretraining on the corpus, and the length bias between political families.

\item {\bf Theory assumptions and proofs}
    \item[] Answer: \answerNA{}
    \item[] Justification: This paper is empirical and does not include theoretical results.

\item {\bf Experimental result reproducibility}
    \item[] Answer: \answerYes{}
    \item[] Justification: All hyperparameters, data splits, and model choices are described. Code is provided in the GitHub repository.

\item {\bf Open access to data and code}
    \item[] Answer: \answerYes{}
    \item[] Justification: Code is available on GitHub. The corpus is publicly available through the Archelec project.

\item {\bf Experimental setting/details}
    \item[] Answer: \answerYes{}
    \item[] Justification: Section~\ref{sec:models} describes all training parameters (TF-IDF settings, CamemBERT learning rate / batch size / epochs / optimizer / scheduler, logistic regression regularisation and class weights). Appendix~\ref{app:training} lists the CamemBERT configurations we tried before the final one.

\item {\bf Experiment statistical significance}
    \item[] Answer: \answerYes{}
    \item[] Justification: TF-IDF and the linear probe are evaluated with 5-fold stratified cross-validation on train+val (mean $\pm$ s.d.\ reported, Table~\ref{tab:results}), and re-evaluated under a year-based temporal split (train $\leq$ 1981, test $\geq$ 1988; Table~\ref{tab:temporal}). CamemBERT fine-tuning uses a single seeded run because of training time.

\item {\bf Experiments compute resources}
    \item[] Answer: \answerYes{}
    \item[] Justification: Appendix~\ref{app:implementation} reports the hardware used (Apple M-series, MPS backend) and approximate training times for each component of the pipeline.

\item {\bf Code of ethics}
    \item[] Answer: \answerYes{}
    \item[] Justification: The research uses publicly available historical documents and does not raise ethical concerns.

\item {\bf Broader impacts}
    \item[] Answer: \answerNA{}
    \item[] Justification: This is an academic study of historical political texts with no direct deployment implications.

\item {\bf Safeguards}
    \item[] Answer: \answerNA{}
    \item[] Justification: The models are trained on public historical data and pose no misuse risk.

\item {\bf Licenses for existing assets}
    \item[] Answer: \answerYes{}
    \item[] Justification: The Archelec corpus is cited and its source URL provided. CamemBERT is cited with its original publication.

\item {\bf New assets}
    \item[] Answer: \answerNA{}
    \item[] Justification: No new datasets or models are released.

\item {\bf Crowdsourcing and research with human subjects}
    \item[] Answer: \answerNA{}
    \item[] Justification: No human subjects were involved.

\item {\bf Institutional review board (IRB) approvals or equivalent for research with human subjects}
    \item[] Answer: \answerNA{}
    \item[] Justification: No human subjects were involved.

\item {\bf Declaration of LLM usage}
    \item[] Answer: \answerNA{}
    \item[] Justification: No LLM is used as a component of the core methodology. CamemBERT is a pretrained encoder model fine-tuned for classification, not used as a generative LLM.

\end{enumerate}
